### 2013-01-04 ISMB/methods_ISMB.tex
RNAPyroEx backtrack buggy
fixed ISMB headers

%!TEX root = main_RECOMB.tex
\section{Methods}
\label{sec:methods}

\newcommand{\PE}[1]{E(#1)}
\newcommand{\EI}{\text{EI}}
\newcommand{\ES}{\text{ES}}
\newcommand{\ISO}{\text{ISO}}
We introduce a probabilistic model, which aims at capturing both the stability of the folded RNA and its ability to adopt a predefined 3D conformation.
To that purpose, a Boltzmann weighted distribution is used, based on a pseudo-energy function $\PE{\cdot}$ which includes contributions for both the free-energy and its putative isostericity towards a multiple sequence alignment. In this model, the probability that the nucleotide at a given position needs to be mutated (i.e. corresponds to a sequencing error) can be computed using a variant of the \emph{Inside-Outside algorithm}~\cite{Lari1990}.

>>>>

%!TEX root = main_ISMB.tex
\section{Methods}
\label{sec:methods}

\newcommand{\PE}[1]{E(#1)}
\newcommand{\EI}{\text{EI}}
\newcommand{\ES}{\text{ES}}
\newcommand{\ISO}{\text{ISO}}
We introduce a probabilistic model, aiming to design RNA sequences with a 
specific $\Gb+\Cb$ content, folding into a predefined 2D conformation.
We use a Boltzmann weighted distribution based on a pseudo-energy function 
$\PE{\cdot}$ taking into accounts stacked canonical base pairs free-energy.

%To that purpose, a Boltzmann weighted distribution is used, based on a pseudo-energy function $\PE{\cdot}$ which includes contributions for both the free-energy and its putative isostericity towards a multiple sequence alignment. In this model, the probability that the nucleotide at a given position needs to be mutated (i.e. corresponds to a sequencing error) can be computed using a variant of the \emph{Inside-Outside algorithm}~\cite{Lari1990}.
